\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-10-26 manuscript/ms_MicroMeso.Rnw
fixed font size in ms; updated plot in script

\title{\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change}
\author[]{\large Andrew T. Tredennick} 
\author[]{\large Peter B. Adler}
\affil[]{\footnotesize \emph{Department of Wildland Resources and the Ecology Center, Utah State University}}
\maketitle

@@

\noindent{}\footnotesize{\textbf{Keywords:} population model, forecasting, integral projection model, etc.}

>>>>

\title{\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change}
\author[]{\large Andrew T. Tredennick} 
\author[]{\large Peter B. Adler}
\affil[]{\footnotesize{\emph{Department of Wildland Resources and the Ecology Center, Utah State University}}}
\maketitle

@@

\noindent{}\textbf{Keywords:} population model, forecasting, integral projection model, etc.
